\documentclass[a4paper]{article}
\usepackage{wallpaper}
\CenterWallPaper{1}{UChicagoCHD-letterhead-PG1.pdf}
\usepackage[left=2.5cm,top=8.5cm,right=2.5cm,bottom=3cm,bindingoffset=0cm]{geometry}
\pagenumbering{gobble}
\begin{document}

\noindent 1 July 2022

\vspace{1 cm}

\noindent Dear Dr. Smetana,

\medskip
\medskip

Thank you very much for your invitation to submit an article to \textit{Child Development Perspectives}. I attach herewith my manuscript entitled ``Learning language \textit{in vivo}''. Its main contributions are twofold. First, it serves as an overview of current approaches and findings relevant to children's linguistic input. Second, it presents an alternative approach for thickening our increasingly thin notions of how children actually encounter language in their everyday lives. When outlining this manuscript I kept in mind the connections that could be made between two other recent \textit{Perspectives} manuscripts by Masek et al. (2021) and by Houston (2022). I am glad to have the opportunity to be in conversation with these other works. The manuscript is 3230 words long and has two figures and 40 references cited. I will note that one of the figures includes images that I already plan to replace with simplified line drawings to make the image visually cleaner. I will provide this newer figure version along with any other requested changes in a resubmission.

\medskip

Thank you very much again for the opportunity to share my perspective on this topic. I am looking forward to receiving feedback.

\bigskip
\bigskip
\bigskip

\noindent Sincerely,
\bigskip
\bigskip
\bigskip
\bigskip

\noindent Marisa Casillas

\noindent Assistant Professor,

\noindent Comparative Human Development

\noindent University of Chicago

\noindent mcasillas$@$uchicago.edu
\end{document}